---
title: "p8105_hw5_jd3924"
author: "Jiahe Deng"
date: "2022-11-07"
output: github_document
---

```{r}
library(tidyverse)
```

```{r}
urlfile = "https://raw.githubusercontent.com/washingtonpost/data-homicides/master/homicide-data.csv"
homicides_data = read_csv(url(urlfile), na = c(" ", "Unknown"))
```
In this data, there is 52179 observations and 12 variables.
This data include each case's detailed information, such as victim's name(victim_first,victim_race), age(victim_age),gender(victim_sex), race(victim_race),location(city, state, lat, lon), the progress of the case(disposition), case's reported data(reported_date).
```{r}
homicides_data = 
  homicides_data %>%
  mutate(
    city_state = str_c(city,state, sep = ","),
    case_status = ifelse(disposition %in% c("Closed without arrest","Open/No arrest"), "unsolved","solved")
         ) %>% relocate(city_state) %>% 
  filter(city_state != "Tulsa,AL")
homicides_data
```
```{r}
homicides_data %>%
  group_by(city_state) %>%
  summarize(
    number_of_unsolved = sum(case_status=="unsolved"),
    number_of_homicides = n())
```
```{r}
baltimore_data = 
  homicides_data %>%
  filter(city_state == "Baltimore,MD")

baltimore_summary = 
  baltimore_data %>%
  summarise(
    unsolved_md = sum(case_status == "unsolved"),
    num = n())

prop.test(
  x = baltimore_summary %>% pull(unsolved_md),
  n = baltimore_summary %>% pull(num)
  ) %>%
  broom::tidy()
```
```{r}
prop_test = function(city){
  
  city_summary = 
    city %>% 
      summarise(
        unsolved = sum(case_status == 'unsolved'),
        n = n()
      )
  
  city_test = 
    prop.test(
      x = city_summary %>% pull(unsolved),
      n = city_summary %>% pull(n)
    )
  
  city_test
}
```
```{r} 
#use Baltimore to test whether the function works
prop_test(baltimore_data)
```

```{r}
statistic_df =
  homicides_data %>%
  nest(-city_state) %>%
  mutate(
    result = map(data, prop_test),
    tidy_data = map(result, broom::tidy)
  ) %>%
  select(city_state, tidy_data) %>%
  unnest(tidy_data) %>%
  select(city_state, estimate, starts_with("conf"))
statistic_df
```
```{r}
statistic_df %>%
  mutate(city_state = fct_reorder(city_state, estimate,.desc = TRUE)) %>%
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1)) +
  labs(
    title = "proportion of unsolved homicides",
    x = "location: city,state",
    y = "estimated proportion of unsolved homicides",
    caption = "Data from the Washington Post")
```

```{r}
set.seed(1)
#Conduct a hypothesis T test for n = 30, sigma = 5
sim_mean_sd = function(n, mu, sigma) {
     sample_x = rnorm(n, mean = mu, sd = sigma)
     t_test = t.test(sample_x, conf.int = 0.95) %>%
       broom::tidy() %>%
       select(estimate, p.value)
     
     return(t_test)
}
output = vector("list", 5000)
for (i in 1:5000) {
  output[[i]] = sim_mean_sd(n = 30, mu = 0, sigma = 5)
}
output %>% bind_rows()
```

```{r}
#when mu={1,2,3,4,5,6}
results_df =
  tibble(mu = c(0, 1, 2, 3, 4, 5, 6)) %>%
  mutate(
    results = map(.x = mu, ~rerun(5000, sim_mean_sd(n=30,mu=.x,sigma=5))),
    estimated = map(results, bind_rows)) %>%
  unnest(estimated) %>%
  select(mu, estimate, p.value)
results_df
```


```{r}
power_test =
  results_df %>%
  mutate(
    reject = ifelse(p.value < 0.05, 1, 0)
      ) %>%
  group_by(mu) %>%
  summarize(
    n_reject = sum(reject),
    prop_reject = n_reject / n()
    ) %>%
  rbind()
power_test

power_test_plot =
  power_test %>%
  ggplot(aes(x = mu, y = prop_reject)) +geom_point(aes(color = mu), alpha = 0.5) +
  geom_smooth(alpha = 0.5) +
  theme(legend.position = "bottom") +
  labs(
    title = "plot of proportion of times the null was rejected vs true value of mu",
    x = "mu",
    y = "proportion of times the null was rejected") 
power_test_plot
```
From the plot above, we can see that there is positive relationship between the plot of proportion of times the null was rejected and the true mean, which means the proportion increase as the true mean increase, and the power of test increase too.


